---
title: "A Searchable Database of Philadelphia City Commissioners Potentially Incorrect Ballots"
date: '2024-11-4'
output: 
  html_document:
    toc: true
    toc_float: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
library(DT)
library(readxl)
library(kableExtra)

# Load data in four steps for four xlsx files

# URL to object "url1" - "No Signature"
url1 <- "https://vote.phila.gov/media/2024_General_Election_Deficiency_List_.xlsx"

# Use httr to write the object to a temp file on disk
GET(url1, write_disk(tf1 <- tempfile(fileext = ".xlsx")))

# Read the file using readxl package, attach the name given by the PHL
# City Commissioners to this file as a column
df <- read_excel(tf1) 

```

# What is this document?

**You can use this site to to see if your 2024 mail-in ballot for the November election was listed as "potentially flawed" by the Philadelphia City Commissioners (as of November 4th, 2024) and in need of correction.**

For information about how to correct your ballot, [please visit the Philadelphia City Commissioners' website](https://vote.phila.gov/news/2024/10/08/2024-general-election-unverifiable-identification-undeliverable-and-or-potentially-flawed-ballots/).

On November 1st, 2024, the Philadelphia City Commissioners publicly published pdf and Excel formatted lists of ballots that might be "potentially incorrect" for various reasons. Their [announcement read](https://vote.phila.gov/news/2024/10/08/2024-general-election-unverifiable-identification-undeliverable-and-or-potentially-flawed-ballots/):

*"The Philadelphia Board of Elections has received mail-in and absentee ballots with various issues that may prevent them from being counted in the upcoming November 5, 2024 General Election. These issues include:*

*- Unverifiable Identification: Mail ballots from voters whose identification could not be verified. Voters who have not submitted acceptable proof of ID or whose ID could not be verified should fill out the ID verification form, and submit it along with a photocopy or picture of an acceptable ID (if available) to phillyelection@phila.gov or via fax to (215) 686-3398 by Tuesday, November 12, 2024. Without this information, the Board cannot count your ballot.*

*- Undeliverable or Potentially Flawed: Ballots returned by the U.S. Postal Service as “undeliverable”, or administratively determined to be potentially flawed. Flaws may include lacking a signature on the declaration envelope, lacking a written date on the declaration envelope, lacking a secrecy envelope, or having a potentially incorrect date. These ballot submissions have the possibility of NOT being counted."*

There are also instructions on the Commissioners site for people who cannot appear in person.

This site formats the Commissioners' data in a searchable tool.

# Search for your ballot

Search the database below to see if your ballot was flagged.

```{r datatable, echo=FALSE}
datatable(df, 
          options = list(pageLength = 10))
```
**Attribution and Sourcing**

This tool was created by Michael Fichman on 11/4/2024 using data published by the City Commissioners on 11/1/2024. The code is available [on Github](https://github.com/mafichman/PotentiallyIncorrectBallots).

This tool points directly to the URLs published by the City Commissioners. This site is not associated with the City Commissioners, any government, political party, political action committee, or any election entity.