---
title: "Is My Ballot Incorrect? A Searchable Database of Philadelphia City Commissioners Potentially Incorrect Ballots"
date: '2022-11-07'
output: 
  html_document:
    toc: true
    toc_float: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
library(DT)
library(readxl)
library(kableExtra)

# Load data in four steps for four xlsx files

# URL to object "url1" - "No Signature"
url1 <- "https://vote.phila.gov/files/announcements/11_4_2022_No_signature.xlsx"

# Use httr to write the object to a temp file on disk
GET(url1, write_disk(tf1 <- tempfile(fileext = ".xlsx")))

# Read the file using readxl package, attach the name given by the PHL
# City Commissioners to this file as a column
df1 <- read_excel(tf1) %>%
  mutate(Issue = "No Signature")

# Repeat for file 2 - No Date
url2 <- "https://vote.phila.gov/files/announcements/11_4_2022_No_Date.xlsx"

GET(url2, write_disk(tf2 <- tempfile(fileext = ".xlsx")))

df2 <- read_excel(tf2) %>%
  mutate(Issue = "No Date")

# Repeat for file 3 - Potentially Incorrect Date
url3 <- "https://vote.phila.gov/files/announcements/11_4_2022_Potentially_Incorrect.xlsx"

GET(url3, write_disk(tf3 <- tempfile(fileext = ".xlsx")))

df3 <- read_excel(tf3) %>%
  mutate(Issue = "Potentially incorrect date")

# Repeat for file 4 - Naked Ballots

url4 <- "https://vote.phila.gov/files/announcements/11_4_2022_Naked.xlsx"

GET(url4, write_disk(tf4 <- tempfile(fileext = ".xlsx")))

df4 <- read_excel(tf4) %>%
  mutate(Issue = "Not enclosed in a Secrecy Envelope (a.k.a. Naked Ballots)")

# Bind the data sets together
dat <- rbind(df1, df2) %>%
  rbind(., df3) %>%
  rbind(., df4)

```

# What is this document?

You can use the table below to search the data published by the Philadelphia City Commissioners to see if your 2022 mail-in ballot for the November election was listed as "potentially incorrect" and in need of correction. 

For information about how to correct your ballot, [please visit the Philadelphia City Commissioners' website](https://vote.phila.gov/news/2022/11/05/ballots-administratively-determined-to-have-no-secrecy-envelope-or-no-signature-no-date-or-a-potentially-incorrect-date-on-return-envelope/).

On November 5th, 2022, the Philadelphia City Commissioners publicly published lists of ballots that might be "Potentially Incorrect" for various reasons. [They published 4 pdf and 4 Excel files to their website](https://vote.phila.gov/news/2022/11/05/ballots-administratively-determined-to-have-no-secrecy-envelope-or-no-signature-no-date-or-a-potentially-incorrect-date-on-return-envelope/) with lists of mail-in-ballots that had potential problems. The [announcement read](https://vote.phila.gov/news/2022/11/05/ballots-administratively-determined-to-have-no-secrecy-envelope-or-no-signature-no-date-or-a-potentially-incorrect-date-on-return-envelope/):

*"all these ballot submissions have the possibility of NOT being counted. It is strongly advised that the voters on these lists request a replacement ballot at the County Board of Elections office in City Hall Room 140 on Saturday or Sunday from 9:00 am – 3:00 pm; Monday, November 7th from 9:00 am – 5:00 pm; or on Election Day from 7:30 am – 7:30 pm to avoid the potential rejection of their ballot."*

The databases they published were not searchable in a web browser. This site formats the data in a searchable tool.

This tool points directly to the URLs published by the City Commissioners. The code used to generate this searchable database [is open source and available](https://github.com/mafichman/PotentiallyIncorrectBallots).
This site is not associated with the City Commissioners, any government, or any election entity.

# Searchable Database

```{r datatable, echo=FALSE}
datatable(dat, 
          options = list(pageLength = 10))
```
**Attribution and Sourcing**

This tool was created by Michael Fichman on 11/7/2022 using data published by the City Commissioners on 11/5/2022. The code is available [on Github](https://github.com/mafichman/PotentiallyIncorrectBallots).